---
title: "HW_2"
author: "AJM170007"
date: "November 1, 2018"
output: html_document
---


```{r}
#Lets load some packages

library(dplyr)
library(ggplot2)
library(caret)

#Lets load the dataset#
s <- read.csv("SystemAdministrators.csv",header = T,stringsAsFactors = F) 

##Lets create a scatterplot##
color.codes<-as.character(c("#3399FF", "#FF0000"))
color.names<-c("blue", "red")
Completed.task <- c("Yes","No")
df2 <- data.frame(Completed.task, color.codes, color.names)
df <-merge(s,df2, by=("Completed.task"), all.x=TRUE, all.y=TRUE)
 ggplot(data = df, aes(Experience, Training , colour = Completed.task))+ 
  geom_point() +
  scale_colour_manual(breaks = df$Completed.task, 
                      values = unique(as.character(df$color.codes)))+
 ggtitle("Experience VS Training") +
  xlab("Experience") + ylab("Training")


```


**1) We can see from the above scatterplot that Experience appears potentially useful for classifying task completion because a higher percentage of the blue points which represents people who have completed tasks are present for experience>8 with training credits being 4**   

```{r}

##Lets run a logistic model using the entire data as the training dataset##

df <- df[1:3]
df$Completed.task <- ifelse(df$Completed.task=="Yes",1,0)
logit.reg <- glm( Completed.task~ ., data = df, family = "binomial") 
summary(logit.reg)
pred <- as.data.frame(predict(logit.reg, type="response"))
colnames(pred)[1] <- "Pred"
pred$pred_class <- ifelse(pred$Pred>0.5,1,0)
df <- cbind(df,pred)
df$pred_class <- as.factor(df$pred_class)
df$Completed.task <- as.factor(df$Completed.task)

```
```{r}
###Confusion matrix##
confusionMatrix(data=df$pred_class,df$Completed.task)

```

```{r}

##Percentage of misclassified  programmers incorrectly classified as failing to complete the task#

(5/15)*100

```


**2) Conclusion- It can be seen that,Among those who completed the task,33.33% of the programmers were incorrectly classified**


**3)Logistic Regression equation**

$log(odds) = -10.9813 + ( 1.1269 * Experience) + ( 0.1805 * Training)$

**Where odds=0.6,Training=6**

**Experience= 9.2364**

**Conclusion:9.2364 years of experience should be accumulated by the programmer with 6 Training credits before his estimated probability of completing the tasks exceeds 0.6** 

