---
title: "Support Vector Machine"
subtitle: "(using e1071 package)"
author: ""
date: "January 30, 2019"
output: 
  html_document: 
    theme: cerulean
---


```{r loadpackages, include = FALSE}
library(e1071)
library(ggplot2)
library(caret)
library(rmarkdown)
library(corrplot)
options(digits = 3)
```

```{r readdata}
data(iris)
dim(iris)
str(iris)
```

_Drop Species variable  and check correlation:_
```{r correlationplot}
iris4 <- iris[, -5]
cor(iris4)
corrplot(cor(iris4), method = "color", type = "upper", tl.srt = 45)
```


_Check relationship between sepal length and width:_
```{r lengthwidthplot1}
ggplot(data=iris) +
  geom_point(aes(x= Sepal.Length, y= Sepal.Width, color = Species))+
  theme_classic()
```

_Check relationship between petal length and width:_
```{r lengthwidthplot2}
ggplot(data=iris) +
  geom_point(aes(x= Petal.Length, y= Petal.Width, color = Species))+
  theme_classic()
```


_Create data partition:_
```{r datapartition}
set.seed(123)
trainindex <- createDataPartition(iris$Species, p=0.8, list= FALSE)
iris_train <- iris[trainindex, ]
iris_test <- iris[-trainindex, ]
```


### SVM Model  
```{r modeling}
svm1 <- svm(Species~., data=iris_train)
summary(svm1)
plot(svm1, data=iris_train, Petal.Width~Petal.Length,
     slice = list(Sepal.Width = 3, Sepal.Length = 5),
     color.palette = terrain.colors)

 ## Performance Evaluation ##
pred1 <- predict(svm1, iris_test)

    # confusion matrix
conf.matrix <- table(Predicted = pred1, Actual = iris_test$Species)
conf.matrix
  
    # accuracy
(sum(diag(conf.matrix))) / sum(conf.matrix)
```


Change Kernel used in  SVM model 
svm2 <- svm(Species~., data=iris_train, kernel = "linear")
svm3 <- svm(Species~., data=iris_train, kernel = "polynomial")
svm4 <- svm(Species~., data=iris_train, kernel = "sigmoid")


### Hyperparameter Optimization 
```{r hyperparametertuning}
  

set.seed(123)
tunesvm1 <- tune(svm, Species~., data = iris_train,
     ranges = list(epsilon = seq(0,1,0.1), cost = 2^(2:7)))

summary(tunesvm1)
plot(tunesvm1)


  ## Best SVM Model ##
bestsvm1 <- tunesvm1$best.model
summary(bestsvm1)
plot(bestsvm1, data=iris_train, Petal.Width~Petal.Length,
     slice = list(Sepal.Width = 3, Sepal.Length = 5),
     color.palette = terrain.colors)

bestpred1 <- predict(bestsvm1, iris_test)

# confusion matrix
conf.matrix2 <- table(Predicted = bestpred1, Actual = iris_test$Species)
conf.matrix2

  # accuracy
(sum(diag(conf.matrix2))) / sum(conf.matrix2)

```

